Running the simulation

### 2016-02-04 drafts/hybrid_zone.tex

\section{Methods}
\subsection{Model}
We consider a model in which two isolated subspecies, species $A$ and species $B$ come into contact at time $\tau$ generations in the past. Individuals move forward in time by sampling a displacement from a Gaussian distribution. In the simplest case of under-dominance, the fitness of an individual is determined by its genotype at a particular locus $L$, such that individuals that are heterozygous at locus $L$ have fitness reduced by $s>0$ compared to homozygotes.

@@

%%%%%%%% %%%%%%%%%%
\subsection{Analysis}

@@

%%%%%%%% %%%%%%%%%%
\subsection{Simulations}
Forward in time simulations were used to assess theoretical predictions. We simulate discrete demes with nearest-neighbor migration and non-overlapping generations. Each generation, the dispersal distance of an individual is sampled from a normal distribution, and then discretized to correspond to a deme that is a corresponding distance away. Following migration, the next generation is produced by replacing each individual in a deme by randomly choosing two parents with probability weighted by the fitness of their genotypes. The genotype of the new individual is generated by simulating a recombined chromosome from each parent. This simulation keeps track of the ancestry at each location in the chromosome for all individuals. Each individual has 2 pairs of chromosomes each of length 1 Morgan such that chromosome 1 contains a selected locus at position 0.5M, and chromosome 2 contains no selected loci.

@@

\subsection{Statistics}
With the above theory and simulations, we are able to make predictions about patterns surrounding selected loci. In reality, however, such loci are not known, so it is useful to have per-site statistics that may allow for detection of candidate targets of selection. The most straightforward measure is $l_I(b)$ the length of haplotype chunk that a sampled chunk containing genomic position $b$, conditioned on ancestry $I$ at the site.

@@

%\subsection{Data}
%We compare the predictions of our model to genomic data obtained from individuals sampled a naturally occurring hybrid zone between \emph{Mus m. musculus/M. m. domesticus} \cite{Turner2011,Turner2014}. The genomic data generated by \citep{Turner2014} was for a mapping population generated by mating wild-caught individuals. Because some individuals were mated multiple times, the mapping population comprises many closely related individuals. We approximate wild population samples by restricting our analysis to genotyped individuals that had both parents sampled in the same location in such a way that none of the individuals shared a parent (see table for list of individuals). Approximately 280,000 SNPs were represented in the final dataset.

@@

\section{Results}
\subsection{The distribution of ancestry tract lengths}
We are interested specifically in the distribution of the length of continuous tracts of ancestry surrounding the selected locus. Far away from the zone center variants under negative selection will be rare \citep[for demonstration of this theoretical result, see e.g.][]{May1975,Slatkin1973,Barton??}, however, when present an unfit migrant haplotype is expected to be longer than a neutral migrant haplotype. Figure X shows the estimated probability density (pdf), of unbroken tract of ancestry B surrounding the selected locus, conditioning on a haplotype being of ancestry B at the selected locus. Compared to the expected density of tract lengths surrounding neutral loci, tracts of ancestry B around the selected locus are longer.

\subsection{Number of ancestors}
Not sure what the result is here yet -- unexpected

\subsection{Identifying sites under selection}

>>>>

\section{Methods}
\subsection*{Model}
We consider a model in which two isolated subspecies, species $A$ and species $B$ come into contact at time $\tau$ generations in the past. Individuals move forward in time by sampling a displacement from a Gaussian distribution. In the simplest case of under-dominance, the fitness of an individual is determined by its genotype at a particular locus $L$, such that individuals that are heterozygous at locus $L$ have fitness reduced by $s>0$ compared to homozygotes.

@@

%%%%%%%% %%%%%%%%%%
\subsection*{Analysis}

@@

%%%%%%%% %%%%%%%%%%
\subsection*{Simulations}
Forward in time simulations were used to assess theoretical predictions. We simulate discrete demes with nearest-neighbor migration and non-overlapping generations. Each generation, the dispersal distance of an individual is sampled from a normal distribution, and then discretized to correspond to a deme that is a corresponding distance away. Following migration, the next generation is produced by replacing each individual in a deme by randomly choosing two parents with probability weighted by the fitness of their genotypes. The genotype of the new individual is generated by simulating a recombined chromosome from each parent. This simulation keeps track of the ancestry at each location in the chromosome for all individuals. Each individual has 2 pairs of chromosomes each of length 1 Morgan such that chromosome 1 contains a selected locus at position 0.5M, and chromosome 2 contains no selected loci.

@@

\subsection*{Statistics}
With the above theory and simulations, we are able to make predictions about patterns surrounding selected loci. In reality, however, such loci are not known, so it is useful to have per-site statistics that may allow for detection of candidate targets of selection. The most straightforward measure is $l_I(b)$ the length of haplotype chunk that a sampled chunk containing genomic position $b$, conditioned on ancestry $I$ at the site.

@@

%\subsection*{Data}
%We compare the predictions of our model to genomic data obtained from individuals sampled a naturally occurring hybrid zone between \emph{Mus m. musculus/M. m. domesticus} \cite{Turner2011,Turner2014}. The genomic data generated by \citep{Turner2014} was for a mapping population generated by mating wild-caught individuals. Because some individuals were mated multiple times, the mapping population comprises many closely related individuals. We approximate wild population samples by restricting our analysis to genotyped individuals that had both parents sampled in the same location in such a way that none of the individuals shared a parent (see table for list of individuals). Approximately 280,000 SNPs were represented in the final dataset.

@@

\section{Results}
\subsection*{The distribution of ancestry tract lengths}
We are interested specifically in the distribution of the length of continuous tracts of ancestry surrounding the selected locus. Far away from the zone center variants under negative selection will be rare \citep[for demonstration of this theoretical result, see e.g.][]{May1975,Slatkin1973,Barton??}, however, when present an unfit migrant haplotype is expected to be longer than a neutral migrant haplotype. Figure X shows the estimated probability density (pdf), of unbroken tract of ancestry B surrounding the selected locus, conditioning on a haplotype being of ancestry B at the selected locus. Compared to the expected density of tract lengths surrounding neutral loci, tracts of ancestry B around the selected locus are longer.

\subsection*{Number of ancestors}
Not sure what the result is here yet -- unexpected

\subsection*{Identifying sites under selection}

### 2016-02-04 sims/run-sim.Rmd

>>>>

Here `sim` is a list with five named components:

- **inds** is a list of length `ninds`, 
    - each element of which is a list, one element per chromosome,
        - each element of which is a list with names "X1" and "X2", corresponding to the two copies of the chromosome,
            - each element of which is a data frame, with columns:
                - **pos**: coordinates of recombination
                - **ancest**: ancestor ID
- **sp.inds** is a character vector of length `ninds`, giving the ancestral type of each ancestor (i.e., ancestries corresponding to the the ancestor IDs)
- **deme** is an integer vector of length `ninds`, giving the deme number of each individual (including the ancestors)
- **pars** is an integer that gives the number of generations of the simulation
- **QTL** returns the QTL vector used in the simulation

and `sim.sums` is a named list with components:

- **ind.ancestry**: a list of length `ninds`
    - each element of which is a list, one element per chromosome,
        - each element of which is a list with names "X1" and "X2", corresponding to the two copies of the chromosome,
            - each element of which is a data frame, with variables
                - **starts**: start position of a chunk of ancestry
                - **stops**: end position of the chunk of ancestry
                - **sp2**: logical variable saying whether the chunk is of ancestry $A$ or not
- **ancest.prop**: is a `ninds*2` matrix giving the ancestry proportion of each individual on each of their two copies of the chromosome.
